---
title: "Simulation Study"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, error = FALSE)
library(dplyr)
library(ggplot2)
library(ggpubr)
library(plotly)
library(data.table)
```


```{r, include = FALSE}
###### Plot for Power and FP ######
plot_pwr = function(dist,p,df){
    ggplot2::ggplot(df[df$Prop==p & df$Distribution == dist,], aes(SampleSize, power,
                                                                   group = interaction(Test, Distribution),
                                                                   color = Test)) +
      geom_point(aes(size = 2, shape = pwr_range, color = Test)) +
      geom_line() +
      labs(colour = "Test", shape = "Power Range") + 
      scale_shape_manual(values = c("Low" = 20, "Medium" = 9, "High" = 2)) +
      theme(legend.position = 'right') +
      facet_grid(delta_mu ~ sd_inflation,
                 labeller = labeller(delta_mu = delta_mu_labels,
                                     sd_inflation = sd_inflation_labels),scales="free") +
      theme_classic2(14) +
      scale_color_viridis_d() +
      #scale_color_viridis_d(option = "H")+
      ggtitle(paste0("Mixing Proportion =", p))+
      ylab("Power") +
      scale_size(guide="none") +
      ylim(0,max(df$power))
}


plot_fp = function(dist,p,df) {
  ggplot2::ggplot(df[df$Prop==p & df$Distribution == dist,], aes(SampleSize, FP,
                                                      group = interaction(Test, Distribution),
                                                      color = Test)) +
    geom_point(aes(size = 2, shape = fp_range, color = Test)) +
    geom_line() + 
    geom_hline(yintercept = 0.05, linetype = "dashed", color = "red") +
    #annotate(x = 30, y = 0.052, label = "0.05", color = "red", geom = "text") +
    labs(colour = "Test", shape = "False Positive") + 
    scale_shape_manual(values = c("Preserved" = 20, "Slightly Inflated" = 9, "High" = 2)) +
    theme(legend.position = 'right') +
    facet_grid(delta_mu ~ sd_inflation,
                 labeller = labeller(delta_mu = delta_mu_labels,
                                     sd_inflation = sd_inflation_labels),scales="free") +
    theme_classic2(14) +
    scale_color_viridis_d() +
    ggtitle(paste0("Mixing Proportion =", p)) +
    ylab("False Positive Rate") +
    scale_size(guide="none") +
    ylim(0, max(df$FP))
}


plot_pwr_b = function(df){
  ggplot2::ggplot(df, aes(SampleSize, power, group = interaction(Test, Distribution), color = Test)) +
    geom_point(aes(size = 2, shape = pwr_range, color = Test)) +
    geom_line() + 
    labs(colour = "Test", shape = "Power Range") + 
    scale_shape_manual(values = c("Low" = 20, "Medium" = 9, "High" = 2)) +
    theme(legend.position = 'right') +
    facet_grid(s2 ~ s1,
              labeller = labeller(s2 = s2_labels, s1 = s1_labels))+
    theme_classic2(14)+
    scale_color_viridis_d()+
    ylab("Power") +
    scale_size(guide="none") +
    ylim(0,max(df$power))

}


plot_fp_b = function(df){
  ggplot2::ggplot(df, aes(SampleSize, FP, group = interaction(Test, Distribution), color = Test)) +
    geom_point(aes(size = 2, shape = fp_range, color = Test)) +
    geom_line() + 
    geom_hline(yintercept = 0.05, linetype = "dashed", color = "red") +
    scale_y_continuous(breaks = c(0,0.05,0.25,0.50,0.75,1.00), labels = c(0,0.05,0.25,0.50,0.75,1.00), limits = c(0.0,1.0)) +
    labs(colour = "Test", shape = "False Positive") + 
    scale_shape_manual(values = c("Preserved" = 20, "Slightly Inflated" = 9, "High" = 2)) +
    theme(legend.position = 'right') +
    facet_grid(s2 ~ s1, scales = "free",
              labeller = labeller(s2 = s2_labels, s1 = s1_labels)) +
    theme_classic2(14) +
    scale_color_viridis_d() +
    ylab("False Positive Rate") +
    scale_size(guide="none")

}

```


```{r, include = FALSE} 
###### Interactive Plotly ######
plot_pwr_inter = function(dist,p,df){
  p = ggplotly(
  ggplot2::ggplot(df[df$Prop==p & df$Distribution == dist,], aes(SampleSize, power,
                                                                 group = interaction( Test, Distribution),
                                                                 color = Test)) +
    geom_point(aes(size = 2, shape = pwr_range, color = Test)) +
    geom_line() +
    labs(colour = "Test", shape = "Power Range") + 
    scale_shape_manual(values = c("Low" = 20, "Medium" = 9, "High" = 2)) +
    theme(legend.position = 'right') +
    facet_grid(delta_mu ~ sd_inflation,
               labeller = labeller(delta_mu = delta_mu_labels,
                                   sd_inflation = sd_inflation_labels),scales="free") +
    theme_classic2(14) +
    scale_color_viridis_d() +
    #scale_color_viridis_d(option = "H")+
    ggtitle(paste0("Mixing Proportion =", p))+
    ylab("Power") +
    scale_size(guide="none") +
    ylim(0,max(df$power))
  )
  
  df= data.frame(id = seq_along(p$x$data), legend_entries = unlist(lapply(p$x$data, `[[`, "name")))
  df$legend_group <- sapply(df$legend_entries, function(x) strsplit(gsub("^\\(|\\)$", "", x),",")[[1]][1])
  df$is_first <- !duplicated(df$legend_group)
  
  for (i in df$id) {
    # Is the layer the first entry of the group?
    is_first <- df$is_first[[i]]
    # Assign the group identifier to the name and legendgroup arguments
    p$x$data[[i]]$name <- df$legend_group[[i]]
    p$x$data[[i]]$legendgroup <- p$x$data[[i]]$name
    # Show the legend only for the first layer of the group 
    if (!is_first) p$x$data[[i]]$showlegend <- FALSE
  }
return (p)
}  
  
  
plot_fp_inter = function(dist,p,df){
  p = ggplotly(
  ggplot2::ggplot(df[df$Prop==p & df$Distribution == dist,], aes(SampleSize, FP,
                                                      group = interaction(Test, Distribution),
                                                      color = Test)) +
    geom_point(aes(size = 2, shape = fp_range, color = Test)) +
    geom_line() + 
    geom_hline(yintercept = 0.05, linetype = "dashed", color = "red") +
    #annotate(x = 30, y = 0.052, label = "0.05", color = "red", geom = "text") +
    labs(colour = "Test", shape = "False Positive") + 
    scale_shape_manual(values = c("Preserved" = 20, "Slightly Inflated" = 9, "High" = 2)) +
    theme(legend.position = 'right') +
    facet_grid(delta_mu ~ sd_inflation,
                 labeller = labeller(delta_mu = delta_mu_labels,
                                     sd_inflation = sd_inflation_labels),scales="free") +
    theme_classic2(14) +
    scale_color_viridis_d() +
    ggtitle(paste0("Mixing Proportion =", p)) +
    ylab("False Positive Rate") +
    scale_size(guide="none") +
    ylim(0,max(df$FP))
  )
  
  df= data.frame(id = seq_along(p$x$data), legend_entries = unlist(lapply(p$x$data, `[[`, "name")))
  df$legend_group <- sapply(df$legend_entries, function(x) strsplit(gsub("^\\(|\\)$", "", x),",")[[1]][1])
  df$is_first <- !duplicated(df$legend_group)
  
  for (i in df$id) {
    # Is the layer the first entry of the group?
    is_first <- df$is_first[[i]]
    # Assign the group identifier to the name and legendgroup arguments
    p$x$data[[i]]$name <- df$legend_group[[i]]
    p$x$data[[i]]$legendgroup <- p$x$data[[i]]$name
    # Show the legend only for the first layer of the group 
    if (!is_first) p$x$data[[i]]$showlegend <- FALSE
  }
return (p)
}  

plot_pwr_b_inter = function(df){
  p = ggplotly(
  ggplot2::ggplot(df, aes(SampleSize, power, group = interaction(Test, Distribution), color = Test)) +
    geom_point(aes(size = 2, shape = pwr_range, color = Test)) +
    geom_line() + 
    labs(colour = "Test", shape = "Power Range") + 
    scale_shape_manual(values = c("Low" = 20, "Medium" = 9, "High" = 2)) +
    theme(legend.position = 'right') +
    facet_grid(s2 ~ s1,
              labeller = labeller(s2 = s2_labels, s1 = s1_labels),scales="free")+
    theme_classic2(14)+
    scale_color_viridis_d()+
    ylab("Power") +
    scale_size(guide="none") +
    ylim(0,max(df$power))
  )
  
  df= data.frame(id = seq_along(p$x$data), legend_entries = unlist(lapply(p$x$data, `[[`, "name")))
  df$legend_group <- sapply(df$legend_entries, function(x) strsplit(gsub("^\\(|\\)$", "", x),",")[[1]][1])
  df$is_first <- !duplicated(df$legend_group)
  
  for (i in df$id) {
    # Is the layer the first entry of the group?
    is_first <- df$is_first[[i]]
    # Assign the group identifier to the name and legendgroup arguments
    p$x$data[[i]]$name <- df$legend_group[[i]]
    p$x$data[[i]]$legendgroup <- p$x$data[[i]]$name
    # Show the legend only for the first layer of the group 
    if (!is_first) p$x$data[[i]]$showlegend <- FALSE
  }
return (p)
}  

plot_fp_b_inter = function(df){
  p = ggplotly(
  ggplot2::ggplot(df, aes(SampleSize, FP, group = interaction(Test, Distribution), color = Test)) +
    geom_point(aes(size = 2, shape = fp_range, color = Test)) +
    geom_line() + 
    geom_hline(yintercept = 0.05, linetype = "dashed", color = "red") +
    scale_y_continuous(breaks = c(0,0.05,0.25,0.50,0.75,1.00), labels = c(0,0.05,0.25,0.50,0.75,1.00), limits = c(0.0,1.0)) +
    labs(colour = "Test", shape = "False Positive") + 
    scale_shape_manual(values = c("Preserved" = 20, "Slightly Inflated" = 9, "High" = 2)) +
    theme(legend.position = 'right') +
    facet_grid(s2 ~ s1,
              labeller = labeller(s2 = s2_labels, s1 = s1_labels),scales="free") +
    theme_classic2(14) +
    scale_color_viridis_d() +
    ylab("False Positive Rate") +
    scale_size(guide="none")
)
  df= data.frame(id = seq_along(p$x$data), legend_entries = unlist(lapply(p$x$data, `[[`, "name")))
  df$legend_group <- sapply(df$legend_entries, function(x) strsplit(gsub("^\\(|\\)$", "", x),",")[[1]][1])
  df$is_first <- !duplicated(df$legend_group)
  
  for (i in df$id) {
    # Is the layer the first entry of the group?
    is_first <- df$is_first[[i]]
    # Assign the group identifier to the name and legendgroup arguments
    p$x$data[[i]]$name <- df$legend_group[[i]]
    p$x$data[[i]]$legendgroup <- p$x$data[[i]]$name
    # Show the legend only for the first layer of the group 
    if (!is_first) p$x$data[[i]]$showlegend <- FALSE
  }
return (p)
}  
  

```

```{r, include = FALSE} 
### Power with FP ###
plot_pwr_fp = function(dist,p,df){
  ggplot2::ggplot(df[df$Prop==p & df$Distribution == dist,], aes(SampleSize, power,
                                                                 group = interaction(Test, Distribution),
                                                                 color = Test)) +
    geom_point(aes(size = 2, shape = fp_range, color = Test)) +
    geom_line() +
    labs(colour = "Test", shape = "FP Range") + 
    scale_shape_manual(values = c("Preserved" = 20, "Slightly Inflated" = 9, "High" = 2)) +
    theme(legend.position = 'right') +
    facet_grid(delta_mu ~ sd_inflation,
               labeller = labeller(delta_mu = delta_mu_labels,
                                   sd_inflation = sd_inflation_labels),scales="free") +
    theme_classic2(14) +
    scale_color_viridis_d() +
    ggtitle(paste0("Mixing Proportion =", p))+
    ylab("Power") +
    scale_size(guide="none") +
    ylim(0,max(df$power)) +
    scale_x_continuous(trans = "log2", breaks = c(20, 50, 100, 200, 400), labels = c(20, 50, 100, 200, 400))
}

plot_pwr_fp_b = function(df){
  ggplot2::ggplot(df, aes(SampleSize, power, group = interaction(Test, Distribution), color = Test)) +
    geom_point(aes(size = 2, shape = fp_range, color = Test)) +
    geom_line() + 
    labs(colour = "Test", shape = "FP Range") + 
    scale_shape_manual(values = c("Preserved" = 20, "Slightly Inflated" = 9, "High" = 2)) +
    theme(legend.position = 'right') +
    facet_grid(s2 ~ s1,
              labeller = labeller(s2 = s2_labels, s1 = s1_labels),scales="free")+
    theme_classic2(14)+
    scale_color_viridis_d()+
    ylab("Power") +
    scale_size(guide="none") +
    ylim(0,max(df$power)) +
    scale_x_continuous(trans = "log2", breaks = c(20, 50, 100, 200, 400), labels = c(20, 50, 100, 200, 400))

}

```


```{r, include = FALSE} 
### Power with FP ###
plot_pwr_fp = function(dist,p,df){
  ggplot2::ggplot(df[df$Prop==p & df$Distribution == dist,], aes(SampleSize, power,
                                                                 group = interaction(Test, Distribution),
                                                                 color = Test)) +
    geom_point(aes(size = 2, shape = fp_range, color = Test)) +
    geom_line() +
    labs(colour = "Test", shape = "FP Range") + 
    scale_shape_manual(values = c("Preserved" = 20, "Slightly Inflated" = 9, "High" = 2)) +
    theme(legend.position = 'right') +
    facet_grid(delta_mu ~ sd_inflation,
               labeller = labeller(delta_mu = delta_mu_labels,
                                   sd_inflation = sd_inflation_labels),scales="free") +
    theme_classic2(14) +
    scale_color_viridis_d() +
    ggtitle(paste0("Mixing Proportion =", p))+
    ylab("Power") +
    scale_size(guide="none") +
    ylim(0,max(df$power)) +
    scale_x_continuous(trans = "log2", breaks = c(20, 50, 100, 200, 400), labels = c(20, 50, 100, 200, 400))
}

plot_pwr_fp_b = function(df){
  ggplot2::ggplot(df, aes(SampleSize, power, group = interaction(Test, Distribution), color = Test)) +
    geom_point(aes(size = 2, shape = fp_range, color = Test)) +
    geom_line() + 
    labs(colour = "Test", shape = "FP Range") + 
    scale_shape_manual(values = c("Preserved" = 20, "Slightly Inflated" = 9, "High" = 2)) +
    theme(legend.position = 'right') +
    facet_grid(s2 ~ s1,
              labeller = labeller(s2 = s2_labels, s1 = s1_labels),scales="free")+
    theme_classic2(14)+
    scale_color_viridis_d()+
    ylab("Power") +
    scale_size(guide="none") +
    ylim(0,max(df$power)) +
    scale_x_continuous(trans = "log2", breaks = c(20, 50, 100, 200, 400), labels = c(20, 50, 100, 200, 400))

}

```


```{r, include = FALSE} 
### Power with FP (Interactive) ###
plot_pwr_fp_inter = function(dist,p,df){
  p = ggplotly(
  ggplot2::ggplot(df[df$Prop==p & df$Distribution == dist,], aes(SampleSize, power,
                                                                 group = interaction(Test, Distribution),
                                                                 color = Test)) +
    geom_point(aes(size = 2, shape = fp_range, color = Test)) +
    geom_line() +
    labs(colour = "Test", shape = "FP Range") + 
    scale_shape_manual(values = c("Preserved" = 20, "Slightly Inflated" = 9, "High" = 2)) +
    theme(legend.position = 'right') +
    facet_grid(delta_mu ~ sd_inflation,
               labeller = labeller(delta_mu = delta_mu_labels,
                                   sd_inflation = sd_inflation_labels),scales="free") +
    theme_classic2(14) +
    scale_color_viridis_d() +
    ggtitle(paste0("Mixing Proportion =", p))+
    ylab("Power") +
    scale_size(guide="none") +
    ylim(0,max(df$power)) +
    scale_x_continuous(trans = "log2", breaks = c(20, 50, 100, 200, 400), labels = c(20, 50, 100, 200, 400))
  )
  
  df= data.frame(id = seq_along(p$x$data), legend_entries = unlist(lapply(p$x$data, `[[`, "name")))
  df$legend_group <- sapply(df$legend_entries, function(x) strsplit(gsub("^\\(|\\)$", "", x),",")[[1]][1])
  df$is_first <- !duplicated(df$legend_group)
  
  for (i in df$id) {
    # Is the layer the first entry of the group?
    is_first <- df$is_first[[i]]
    # Assign the group identifier to the name and legendgroup arguments
    p$x$data[[i]]$name <- df$legend_group[[i]]
    p$x$data[[i]]$legendgroup <- p$x$data[[i]]$name
    # Show the legend only for the first layer of the group 
    if (!is_first) p$x$data[[i]]$showlegend <- FALSE
  }
return (p)
}

plot_pwr_fp_b_inter = function(df){
  p = ggplotly(
  ggplot2::ggplot(df, aes(SampleSize, power, group = interaction(Test, Distribution), color = Test)) +
    geom_point(aes(size = 2, shape = fp_range, color = Test)) +
    geom_line() + 
    labs(colour = "Test", shape = "FP Range") + 
    scale_shape_manual(values = c("Preserved" = 20, "Slightly Inflated" = 9, "High" = 2)) +
    theme(legend.position = 'right') +
    facet_grid(s2 ~ s1,
              labeller = labeller(s2 = s2_labels, s1 = s1_labels),scales="free")+
    theme_classic2(14)+
    scale_color_viridis_d()+
    ylab("Power") +
    scale_size(guide="none") +
    ylim(0,max(df$power)) +
    scale_x_continuous(trans = "log2", breaks = c(20, 50, 100, 200, 400), labels = c(20, 50, 100, 200, 400))
   )
  
  df= data.frame(id = seq_along(p$x$data), legend_entries = unlist(lapply(p$x$data, `[[`, "name")))
  df$legend_group <- sapply(df$legend_entries, function(x) strsplit(gsub("^\\(|\\)$", "", x),",")[[1]][1])
  df$is_first <- !duplicated(df$legend_group)
  
  for (i in df$id) {
    # Is the layer the first entry of the group?
    is_first <- df$is_first[[i]]
    # Assign the group identifier to the name and legendgroup arguments
    p$x$data[[i]]$name <- df$legend_group[[i]]
    p$x$data[[i]]$legendgroup <- p$x$data[[i]]$name
    # Show the legend only for the first layer of the group 
    if (!is_first) p$x$data[[i]]$showlegend <- FALSE
  }
return (p)  
}

```

```{r, include = FALSE} 
###### Density Plot ######

### Module 1
# Norm
den_plot_n_mod_1 = function(p,df){
  ggplot2::ggplot() +
    ggplot2::geom_density(data = df[df$prop == p,], ggplot2::aes(x = value,color=Group)) +
    ggplot2::facet_grid(delta_mu ~ sd_inflation,
                        labeller = labeller(delta_mu = delta_mu_labels,
                                            sd_inflation = sd_inflation_labels),scales="free") + 
    ggplot2::theme_classic(14) +
    ggplot2::ylab("Population Density") +
    ggplot2::xlab("Values") +
    ggplot2::theme(legend.text = ggplot2::element_text(10)) +
    ggplot2::ggtitle(paste0("Mixing Proportion = ",p)) +
    # scale_color_viridis_d() +
    #scale_color_manual(values=c("black","red")) 
    theme(plot.title = element_text(hjust = 0))
}

# Weib
den_plot_w_mod_1 = function(p,df){
  ggplot2::ggplot() +
    ggplot2::geom_density(data = df[df$prop == p,], ggplot2::aes(x = value,color=Group)) +
    ggplot2::facet_grid(delta_mu ~ sd_inflation,
                        labeller = labeller(delta_mu = delta_mu_labels,
                                            sd_inflation = sd_inflation_labels),scales="free") + 
    ggplot2::theme_classic(14) +
    ggplot2::ylab("Population Density") +
    ggplot2::xlab("Values") +
    ggplot2::coord_cartesian(xlim = c(quantile(df[df$prop == p,]$value, probs = 0.01), quantile(df[df$prop == p,]$value, probs = 0.99))) +
    ggplot2::theme(legend.text = ggplot2::element_text(10)) +
    ggplot2::ggtitle(paste0("Mixing Proportion = ",p)) +
    # scale_color_viridis_d() +
    #scale_color_manual(values=c("black","red")) 
    theme(plot.title = element_text(hjust = 0))
}

### Module 2
# Norm 
den_plot_n_mod_2 = function(df, p){
  ggplot2::ggplot() +
    ggplot2::geom_density(data = df[df$prop == p,], ggplot2::aes(x = value))+
    ggplot2::facet_grid(delta_mu ~ sd_inflation,
                        labeller = labeller(delta_mu = delta_mu_labels,
                                            sd_inflation = sd_inflation_labels),scales="free")+
    ggplot2::theme_classic(14) +
    ggplot2::ylab("Population Density") +
    ggplot2::xlab("Values") +
    ggplot2::theme(legend.text = ggplot2::element_text(10)) +
    ggplot2::ggtitle(paste0("Mixing Proportion = ",p)) +
    scale_color_viridis_d() +
    theme(plot.title = element_text(hjust = 0))
} 

# Weib
den_plot_w_mod_2 = function(df, p){
  ggplot2::ggplot() +
    ggplot2::geom_density(data = df[df$prop == p,], ggplot2::aes(x = value))+
    ggplot2::facet_grid(delta_mu ~ sd_inflation,
                        labeller = labeller(delta_mu = delta_mu_labels,
                                            sd_inflation = sd_inflation_labels),scales="free")+
    ggplot2::theme_classic(14) +
    ggplot2::ylab("Population Density") +
    ggplot2::xlab("Values") + 
    ggplot2::coord_cartesian(xlim = c(quantile(df[df$prop == p,]$value, probs = 0.01), quantile(df[df$prop == p,]$value, probs = 0.99))) +
    ggplot2::theme(legend.text = ggplot2::element_text(10)) +
    ggplot2::ggtitle(paste0("Mixing Proportion = ",p)) +
    scale_color_viridis_d() +
    theme(plot.title = element_text(hjust = 0))
} 


# beta
den_plot_beta_mod_2 = function(df){
    ggplot2::ggplot() +
      ggplot2::geom_density(data = df, ggplot2::aes(x = value))+
      ggplot2::facet_grid(s2 ~ s1,
                          labeller = labeller(s2 = s2_labels, s1 = s1_labels),scales="free")+
      ggplot2::theme_classic(14) +
      ggplot2::ylab("Population Density") +
      ggplot2::xlab("Values") +
      ggplot2::theme(legend.text = ggplot2::element_text(10)) +
      #ggplot2::ggtitle(paste0("Mixing Proportion = ",p)) +
      scale_color_viridis_d() +
      theme(plot.title = element_text(hjust = 0))
}
```


# Module {.tabset}
## Module 1 (simulations = 5000) {.tabset}
```{r, include = FALSE}
mod_1_nw_res <- as.data.frame(readRDS( '~/Nadeau/module1_n_w_all_tests_sim(5000)_new.rds'))

mod_1_nw_res$delta_mu = round(mod_1_nw_res$mu2 - mod_1_nw_res$mu1,2)
mod_1_nw_res$sd_inflation = round(mod_1_nw_res$sd2/mod_1_nw_res$sd1, 2)

mod_1_nw_res$pwr_range = ifelse(mod_1_nw_res$power <= 0.4,"Low", ifelse(mod_1_nw_res$power <= 0.8, "Medium", "High"))
mod_1_nw_res$pwr_range = factor(mod_1_nw_res$pwr_range, levels = c("High", "Medium","Low"))

mod_1_nw_res$fp_range = ifelse(mod_1_nw_res$FP <= 0.05,"Preserved", ifelse(mod_1_nw_res$FP <= 0.1, "Slightly Inflated", "High"))
mod_1_nw_res$fp_range = factor(mod_1_nw_res$fp_range, levels = c("High", "Slightly Inflated", "Preserved"))

delta_mu_labels <- paste0('Delta mu = ', unique(mod_1_nw_res$delta_mu))
names(delta_mu_labels) <- unique(mod_1_nw_res$delta_mu)

sd_inflation_labels <- paste0('SD Inflation ', unique(mod_1_nw_res$sd_inflation),"x")
names(sd_inflation_labels) <- unique(mod_1_nw_res$sd_inflation)
```


### Normal Distribution {.tabset}
#### Variance {.tabset}
##### Power

```{r, fig.height = 12,fig.width = 12, echo=FALSE}
for(i in unique(mod_1_nw_res$Prop)){
  print(plot_pwr(dist="norm",p= i, mod_1_nw_res[mod_1_nw_res$Test %in% c("Levene","Permutations (MAD)", "Permutations (SD)" , "Permutations (Gini)"),]))
}
```

##### Power (Interactive Plot)

```{r , fig.height=12, fig.width=12, unit='in'}
p1 = plot_pwr_inter(dist="norm",p= 0.25, mod_1_nw_res[mod_1_nw_res$Test %in% c("Levene","Permutations (MAD)", "Permutations (SD)" , "Permutations (Gini)"),])
p2 = plot_pwr_inter(dist="norm",p= 0.5, mod_1_nw_res[mod_1_nw_res$Test %in% c("Levene","Permutations (MAD)", "Permutations (SD)" , "Permutations (Gini)"),])
p3 = plot_pwr_inter(dist="norm",p= 0.75, mod_1_nw_res[mod_1_nw_res$Test %in% c("Levene","Permutations (MAD)", "Permutations (SD)" , "Permutations (Gini)"),])
p1
p2
p3

```

##### False Positive
```{r , fig.height=12, fig.width=12, unit='in'}

for(i in unique(mod_1_nw_res$Prop)){
  print(plot_fp(dist="norm",p= i,mod_1_nw_res[mod_1_nw_res$Test %in% c("Levene","Permutations (MAD)", "Permutations (SD)" , "Permutations (Gini)"),]))
}

```

##### False Positive (Interactive Plot)
```{r , fig.height=12, fig.width=12, unit='in'}
p1 = plot_fp_inter(dist="norm",p= 0.25, mod_1_nw_res[mod_1_nw_res$Test %in% c("Levene","Permutations (MAD)", "Permutations (SD)" , "Permutations (Gini)"),])
p2 = plot_fp_inter(dist="norm",p= 0.5, mod_1_nw_res[mod_1_nw_res$Test %in% c("Levene","Permutations (MAD)", "Permutations (SD)" , "Permutations (Gini)"),])
p3 = plot_fp_inter(dist="norm",p= 0.75, mod_1_nw_res[mod_1_nw_res$Test %in% c("Levene","Permutations (MAD)", "Permutations (SD)" , "Permutations (Gini)"),])
p1
p2
p3
```

##### Power with False Positive
```{r , fig.height=12, fig.width=12, unit='in'}
for(i in unique(mod_1_nw_res$Prop)){
  print(plot_pwr_fp(dist="norm",p= i, mod_1_nw_res[mod_1_nw_res$Test %in% c("Levene","Permutations (MAD)", "Permutations (SD)" , "Permutations (Gini)"),]))
}

```

##### Power with False Positive (Interactive Plot)
```{r , fig.height=12, fig.width=12, unit='in'}
p1 = plot_pwr_fp_inter(dist="norm",p= 0.25, mod_1_nw_res[mod_1_nw_res$Test %in% c("Levene","Permutations (MAD)", "Permutations (SD)" , "Permutations (Gini)"),])
p2 = plot_pwr_fp_inter(dist="norm",p= 0.5, mod_1_nw_res[mod_1_nw_res$Test %in% c("Levene","Permutations (MAD)", "Permutations (SD)" , "Permutations (Gini)"),])
p3 = plot_pwr_fp_inter(dist="norm",p= 0.75, mod_1_nw_res[mod_1_nw_res$Test %in% c("Levene","Permutations (MAD)", "Permutations (SD)" , "Permutations (Gini)"),])
p1
p2
p3

```

#### Means {.tabset}
##### Power
```{r , fig.height=12, fig.width=12, unit='in'}

for(i in unique(mod_1_nw_res$Prop)){
  print(plot_pwr(dist="norm",p= i,mod_1_nw_res[mod_1_nw_res$Test %in% c("ANOVA","Non-Parametric ANOVA","Permutations (Raw)"),]))
}

```

##### Power (Interactive Plot)
```{r , fig.height=12, fig.width=12, unit='in'}
p1 = plot_pwr_inter(dist="norm",p= 0.25,mod_1_nw_res[mod_1_nw_res$Test %in% c("ANOVA","Non-Parametric ANOVA","Permutations (Raw)"),])
p2 = plot_pwr_inter(dist="norm",p= 0.5,mod_1_nw_res[mod_1_nw_res$Test %in% c("ANOVA","Non-Parametric ANOVA","Permutations (Raw)"),])
p3 = plot_pwr_inter(dist="norm",p= 0.75,mod_1_nw_res[mod_1_nw_res$Test %in% c("ANOVA","Non-Parametric ANOVA","Permutations (Raw)"),])
p1
p2
p3
```

##### False Positive
```{r , fig.height=12, fig.width=12, unit='in'}

for(i in unique(mod_1_nw_res$Prop)){
  print(plot_fp(dist="norm",p= i, mod_1_nw_res[mod_1_nw_res$Test %in% c("ANOVA","Non-Parametric ANOVA","Permutations (Raw)"),]))
}

```

##### False Positive (Interactive Plot)
```{r , fig.height=12, fig.width=12, unit='in'}
p1 = plot_fp_inter(dist="norm",p= 0.25,mod_1_nw_res[mod_1_nw_res$Test %in% c("ANOVA","Non-Parametric ANOVA","Permutations (Raw)"),])
p2 = plot_fp_inter(dist="norm",p= 0.5,mod_1_nw_res[mod_1_nw_res$Test %in% c("ANOVA","Non-Parametric ANOVA","Permutations (Raw)"),])
p3 = plot_fp_inter(dist="norm",p= 0.75,mod_1_nw_res[mod_1_nw_res$Test %in% c("ANOVA","Non-Parametric ANOVA","Permutations (Raw)"),])
p1
p2
p3

```
##### Power with False Positive
```{r , fig.height=12, fig.width=12, unit='in'}

for(i in unique(mod_1_nw_res$Prop)){
  print(plot_pwr_fp(dist="norm",p= i,mod_1_nw_res[mod_1_nw_res$Test %in% c("ANOVA","Non-Parametric ANOVA","Permutations (Raw)"),]))
}

```

##### Power with False Positive (Interactive)
```{r , fig.height=12, fig.width=12, unit='in'}
p1 = plot_pwr_fp_inter(dist="norm",p= 0.25,mod_1_nw_res[mod_1_nw_res$Test %in% c("ANOVA","Non-Parametric ANOVA","Permutations (Raw)"),])
p2 = plot_pwr_fp_inter(dist="norm",p= 0.5,mod_1_nw_res[mod_1_nw_res$Test %in% c("ANOVA","Non-Parametric ANOVA","Permutations (Raw)"),])
p3 = plot_pwr_fp_inter(dist="norm",p= 0.75,mod_1_nw_res[mod_1_nw_res$Test %in% c("ANOVA","Non-Parametric ANOVA","Permutations (Raw)"),])
p1
p2
p3
```

#### Density Plot {.tabset}
```{r , fig.height=12, fig.width=12, unit='in'}
params_grid <- rbind(
  expand.grid(
    Distribution = c("norm"),
    Alpha = .05,
    Sim = 1,
    nboot = 100,
    SampleSize = 5000,
    Prop = c(0.25, 0.5, 0.75),
    mu1 = 0,
    sd1 = 1,
    mu2 = c(0, 2, 4),
    sd2 = c(1, 2, 4)),
  expand.grid(
    Distribution = c("weib"),
    Alpha = .05,
    Sim = 1,
    nboot = 100,
    SampleSize = 5000,
    Prop = c(0.25, 0.5, 0.75),
    mu1 = 1,
    sd1 = 1,
    mu2 = c(1,3,5),
    sd2 = c(1,2,4))
)

df_params = data.frame(
  dist = params_grid$Distribution,
  sample_size = params_grid$SampleSize,
  prop = params_grid$Prop,
  mu1 = params_grid$mu1,
  mu2 = params_grid$mu2,
  sd1 = params_grid$sd1,
  sd2 = params_grid$sd2,
  delta_mu = params_grid$mu2 - params_grid$mu1,
  sd_inflation = params_grid$sd2/params_grid$sd1
)

delta_mu_labels <- paste0('Delta mu = ', unique(df_params$delta_mu))
names(delta_mu_labels) <- unique(df_params$delta_mu)

sd_inflation_labels <- paste0('SD Inflation ', unique(df_params$sd_inflation),"x")
names(sd_inflation_labels) <- unique(df_params$sd_inflation)


df_norm = df_params[df_params$dist == "norm",]
data_norm_mod_1 = rbindlist(lapply(seq_len(nrow(df_norm)),
                                   \(i) with(df_norm[i,],
                                             data.frame(df_norm[i,],
                                                        value = c(rnorm(floor(prop*sample_size), mu1, sd1), rnorm(sample_size - floor(prop*sample_size), mu2, sd2)),
                                                        Group = c(rep("Genotype 1",round(sample_size*prop,0)),rep("Genotype 2",round(sample_size*(1-prop),0)))))))

for(prop in unique(data_norm_mod_1$prop)){
  print(den_plot_n_mod_1(prop,data_norm_mod_1))
}
```

### Weibull Distribution {.tabset}
#### Variance {.tabset}
##### Power
```{r , fig.height=12, fig.width=12, unit='in'}
for(i in unique(mod_1_nw_res$Prop)){
  print(plot_pwr(dist="weib", p= i, mod_1_nw_res[mod_1_nw_res$Test %in% c("Levene","Permutations (MAD)", "Permutations (SD)" , "Permutations (Gini)"),]))
}

```

##### Power (Interactive Plot)
```{r , fig.height=12, fig.width=12, unit='in'}
p1 = plot_pwr_inter(dist="weib", p= 0.25, mod_1_nw_res[mod_1_nw_res$Test %in% c("Levene","Permutations (MAD)", "Permutations (SD)" , "Permutations (Gini)"),])
p2 = plot_pwr_inter(dist="weib", p= 0.5, mod_1_nw_res[mod_1_nw_res$Test %in% c("Levene","Permutations (MAD)", "Permutations (SD)" , "Permutations (Gini)"),])
p3 = plot_pwr_inter(dist="weib", p= 0.75, mod_1_nw_res[mod_1_nw_res$Test %in% c("Levene","Permutations (MAD)", "Permutations (SD)" , "Permutations (Gini)"),])
p1
p2
p3

```

##### False Positive

```{r , fig.height=12, fig.width=12, unit='in'}
for(i in unique(mod_1_nw_res$Prop)){
  print(plot_fp(dist="weib", p= i, mod_1_nw_res[mod_1_nw_res$Test %in% c("Levene","Permutations (MAD)", "Permutations (SD)" , "Permutations (Gini)"),]))
}

```

##### False Positive (Interactive Plot)
```{r , fig.height=12, fig.width=12, unit='in'}

p1 = plot_fp_inter(dist="weib", p= 0.25, mod_1_nw_res[mod_1_nw_res$Test %in% c("Levene","Permutations (MAD)", "Permutations (SD)" , "Permutations (Gini)"),])
p2 = plot_fp_inter(dist="weib", p= 0.5, mod_1_nw_res[mod_1_nw_res$Test %in% c("Levene","Permutations (MAD)", "Permutations (SD)" , "Permutations (Gini)"),])
p3 = plot_fp_inter(dist="weib", p= 0.75, mod_1_nw_res[mod_1_nw_res$Test %in% c("Levene","Permutations (MAD)", "Permutations (SD)" , "Permutations (Gini)"),])

p1
p2
p3
```

##### Power with False Positive
```{r , fig.height=12, fig.width=12, unit='in'}

for(i in unique(mod_1_nw_res$Prop)){
  print(plot_pwr_fp(dist="weib", p= i, mod_1_nw_res[mod_1_nw_res$Test %in% c("Levene","Permutations (MAD)", "Permutations (SD)" , "Permutations (Gini)"),]))
}

```

##### Power with False Positive (Interactive Plot)
```{r , fig.height=12, fig.width=12, unit='in'}
p1 = plot_pwr_fp_inter(dist="weib", p= 0.25, mod_1_nw_res[mod_1_nw_res$Test %in% c("Levene","Permutations (MAD)", "Permutations (SD)" , "Permutations (Gini)"),])
p2 = plot_pwr_fp_inter(dist="weib", p= 0.5, mod_1_nw_res[mod_1_nw_res$Test %in% c("Levene","Permutations (MAD)", "Permutations (SD)" , "Permutations (Gini)"),])
p3 = plot_pwr_fp_inter(dist="weib", p= 0.75, mod_1_nw_res[mod_1_nw_res$Test %in% c("Levene","Permutations (MAD)", "Permutations (SD)" , "Permutations (Gini)"),])
p1
p2
p3

```


#### Means {.tabset}
##### Power
```{r , fig.height=12, fig.width=12, unit='in'}

for(i in unique(mod_1_nw_res$Prop)){
  print(plot_pwr(dist="weib",p= i, mod_1_nw_res[mod_1_nw_res$Test %in% c("ANOVA","Non-Parametric ANOVA","Permutations (Raw)"),]))
}
```

##### Power (Interactive Plot)
```{r , fig.height=12, fig.width=12, unit='in'}

p1 = plot_pwr_inter(dist="weib",p= 0.25, mod_1_nw_res[mod_1_nw_res$Test %in% c("ANOVA","Non-Parametric ANOVA","Permutations (Raw)"),])
p2 = plot_pwr_inter(dist="weib",p= 0.5, mod_1_nw_res[mod_1_nw_res$Test %in% c("ANOVA","Non-Parametric ANOVA","Permutations (Raw)"),])
p3 = plot_pwr_inter(dist="weib",p= 0.75, mod_1_nw_res[mod_1_nw_res$Test %in% c("ANOVA","Non-Parametric ANOVA","Permutations (Raw)"),])

p1
p2
p3
```

##### False Positive
```{r , fig.height=12, fig.width=12, unit='in'}

for(i in unique(mod_1_nw_res$Prop)){
  print(plot_fp(dist="weib",p= i, mod_1_nw_res[mod_1_nw_res$Test %in% c("ANOVA","Non-Parametric ANOVA","Permutations (Raw)"),]))
}
```

##### False Positive (Interactive Plot)
```{r, fig.height = 12, fig.width = 12, unit='in'}
p1 = plot_fp_inter(dist="weib",p= 0.25, mod_1_nw_res[mod_1_nw_res$Test %in% c("ANOVA","Non-Parametric ANOVA","Permutations (Raw)"),])
p2 = plot_fp_inter(dist="weib",p= 0.5, mod_1_nw_res[mod_1_nw_res$Test %in% c("ANOVA","Non-Parametric ANOVA","Permutations (Raw)"),])
p3 = plot_fp_inter(dist="weib",p= 0.75, mod_1_nw_res[mod_1_nw_res$Test %in% c("ANOVA","Non-Parametric ANOVA","Permutations (Raw)"),])
p1
p2
p3

#htmltools::tagList(list(p1, p2, p3))
```
##### Power with False Positive
```{r , fig.height=12, fig.width=12, unit='in'}

for(i in unique(mod_1_nw_res$Prop)){
  print(plot_pwr_fp(dist="weib", p= i, mod_1_nw_res[mod_1_nw_res$Test %in% c("ANOVA","Non-Parametric ANOVA","Permutations (Raw)"),]))
}

```

##### Power with False Positive (Interactive Plot)
```{r , fig.height=12, fig.width=12, unit='in'}
p1 = plot_pwr_fp_inter(dist="weib", p= 0.25, mod_1_nw_res[mod_1_nw_res$Test %in% c("ANOVA","Non-Parametric ANOVA","Permutations (Raw)", "Permutations (Gini)"),])
p2 = plot_pwr_fp_inter(dist="weib", p= 0.5, mod_1_nw_res[mod_1_nw_res$Test %in% c("ANOVA","Non-Parametric ANOVA","Permutations (Raw)" , "Permutations (Gini)"),])
p3 = plot_pwr_fp_inter(dist="weib", p= 0.75, mod_1_nw_res[mod_1_nw_res$Test %in% c("ANOVA","Non-Parametric ANOVA","Permutations (Raw)" , "Permutations (Gini)"),])
p1
p2
p3

```


#### Density Plot {.tabset}
```{r, fig.height=12, fig.width=12, unit='in'}
df_weib = df_params[df_params$dist == "weib",]

df_weib$shape1 = mixdist::weibullpar(df_weib$mu1,df_weib$sd1, loc = 0)$shape
df_weib$scale1 = mixdist::weibullpar(df_weib$mu1,df_weib$sd1, loc = 0)$scale
df_weib$shape2 = mixdist::weibullpar(df_weib$mu2,df_weib$sd2, loc = 0)$shape
df_weib$scale2 = mixdist::weibullpar(df_weib$mu2,df_weib$sd2, loc = 0)$scale


data_weib_mod_1 = rbindlist(lapply(seq_len(nrow(df_weib)),
                                   \(i) with(df_weib[i,],
                                             data.frame(df_weib[i,],
                                                        value = c(rweibull(floor(prop*sample_size), scale = scale1, shape = shape1), rweibull(sample_size - floor(prop*sample_size), scale = scale2, shape = shape2)),
                                                        Group = c(rep("Genotype 1",round(sample_size*prop,0)),rep("Genotype 2",round(sample_size*(1-prop),0)))))))

for (prop in unique(data_weib_mod_1$prop)){
  print(den_plot_w_mod_1(prop, data_weib_mod_1))
}
```


## Module 2 (simulations = 1000) {.tabset}
```{r, fig.height=12, fig.width=12, unit='in'}

mod_2_nw_res <- as.data.frame(readRDS( "~/Nadeau/module2_n_w_10_tests_sim(1000).rds"))


mod_2_nw_res$delta_mu = round(mod_2_nw_res$mu2 - mod_2_nw_res$mu1,2)
mod_2_nw_res$sd_inflation = round(mod_2_nw_res$sd2/mod_2_nw_res$sd1, 2)

mod_2_nw_res$pwr_range = ifelse(mod_2_nw_res$power <= 0.4,"Low", ifelse(mod_2_nw_res$power <= 0.8, "Medium", "High"))
mod_2_nw_res$pwr_range = factor(mod_2_nw_res$pwr_range, levels = c("High", "Medium", "Low"))

mod_2_nw_res$fp_range = ifelse(mod_2_nw_res$FP <= 0.05,"Preserved", ifelse(mod_2_nw_res$FP <= 0.1, "Slightly Inflated", "High"))
mod_2_nw_res$fp_range = factor(mod_2_nw_res$fp_range, levels = c("High", "Slightly Inflated", "Preserved"))

delta_mu_labels <- paste0('Delta mu = ', unique(mod_2_nw_res$delta_mu))
names(delta_mu_labels) <- unique(mod_2_nw_res$delta_mu)

sd_inflation_labels <- paste0('SD Inflation ', unique(mod_2_nw_res$sd_inflation),"x")
names(sd_inflation_labels) <- unique(mod_2_nw_res$sd_inflation)

```


### Normal Distribution {.tabset}
#### Power
```{r , fig.height=12, fig.width=12, unit='in'}

for(i in unique(mod_2_nw_res$Prop)){
  print(plot_pwr(dist="norm",p= i,mod_2_nw_res))
}
# htmltools::tagList(list(p1, p2, p3))
```

#### Power (Interactive Plot)
```{r , fig.height=12, fig.width=12, unit='in'}
p1 = plot_pwr_inter(dist="norm",p= 0.25,mod_2_nw_res)
p2 = plot_pwr_inter(dist="norm",p= 0.5,mod_2_nw_res)
p3 = plot_pwr_inter(dist="norm",p= 0.75,mod_2_nw_res)
p1
p2
p3
```

#### False Positive
```{r , fig.height=12, fig.width=12, unit='in'}
for(i in unique(mod_2_nw_res$Prop)){
  print(plot_fp(dist="norm",p= i,mod_2_nw_res))
}

```

#### False Positive (Interactive Plot)
```{r , fig.height=12, fig.width=12, unit='in'}
p1 = plot_fp_inter(dist="norm",p= 0.25, mod_2_nw_res)
p2 = plot_fp_inter(dist="norm",p= 0.5, mod_2_nw_res)
p3 = plot_fp_inter(dist="norm",p= 0.75, mod_2_nw_res)
p1
p2
p3
```
#### Power with False Positive
```{r , fig.height=12, fig.width=12, unit='in'}

for(i in unique(mod_2_nw_res$Prop)){
  print(plot_pwr_fp(dist="norm",p= i,mod_2_nw_res))
}
```

#### Power with False Positive (Interactive Plot)
```{r , fig.height=12, fig.width=12, unit='in'}
p1 = plot_pwr_fp_inter(dist="norm",p= 0.25,mod_2_nw_res)
p2 = plot_pwr_fp_inter(dist="norm",p= 0.5,mod_2_nw_res)
p3 = plot_pwr_fp_inter(dist="norm",p= 0.75,mod_2_nw_res)
p1
p2
p3
```

#### Density Plot
```{r , fig.height=12, fig.width=12, unit='in'}
data_norm_mod_2 = rbindlist(lapply(seq_len(nrow(df_norm)),
                                   \(i) with(df_norm[i,],
                                             data.frame(df_norm[i,],
                                                        value = c(rnorm(floor(prop*sample_size), mu1, sd1), rnorm(sample_size - floor(prop*sample_size), mu2, sd2))))))
for (prop in unique(data_norm_mod_2$prop)){
  print(den_plot_n_mod_2(data_norm_mod_2, prop))
}
```

### Weibull Distribution {.tabset}
#### Power
```{r , fig.height=12, fig.width=12, unit='in'}

for(i in unique(mod_2_nw_res$Prop)){
   print(plot_pwr(dist="weib",p= i,mod_2_nw_res))
 }
# p1 = plot_pwr(dist="weib",p= 0.25,mod_2_nw_res)
# p2 = plot_pwr(dist="weib",p= 0.5,mod_2_nw_res)
# p3 = plot_pwr(dist="weib",p= 0.75,mod_2_nw_res)
# 
# htmltools::tagList(list(p1, p2, p3))

```

#### Power (Interactive Plot)
```{r , fig.height=12, fig.width=12, unit='in'}

p1 = plot_pwr_inter(dist="weib",p= 0.25,mod_2_nw_res)
p2 = plot_pwr_inter(dist="weib",p= 0.5,mod_2_nw_res)
p3 = plot_pwr_inter(dist="weib",p= 0.75,mod_2_nw_res)
p1
p2
p3

```

#### False Positive
```{r , fig.height=12, fig.width=12, unit='in'}

for(i in unique(mod_2_nw_res$Prop)){
   print(plot_fp(dist="weib",p= i,mod_2_nw_res))
 }

```

#### False Positive (Interactive Plot)

```{r , fig.height=12, fig.width=12, unit='in'}

p1 = plot_fp_inter(dist="weib",p= 0.25,mod_2_nw_res)
p2 = plot_fp_inter(dist="weib",p= 0.5,mod_2_nw_res)
p3 = plot_fp_inter(dist="weib",p= 0.75,mod_2_nw_res)
p1
p2
p3
```
#### Power with False Positive
```{r , fig.height=12, fig.width=12, unit='in'}

for(i in unique(mod_2_nw_res$Prop)){
  print(plot_pwr_fp(dist="weib",p= i,mod_2_nw_res))
}
```

#### Power with False Positive (Interactive Plot)
```{r , fig.height=12, fig.width=12, unit='in'}
p1 = plot_pwr_fp_inter(dist="weib",p= 0.25,mod_2_nw_res)
p2 = plot_pwr_fp_inter(dist="weib",p= 0.5,mod_2_nw_res)
p3 = plot_pwr_fp_inter(dist="weib",p= 0.75,mod_2_nw_res)
p1
p2
p3
```

#### Density Plot
```{r , fig.height=12, fig.width=12, unit='in'}
data_weib_mod_2 = rbindlist(lapply(seq_len(nrow(df_weib)),
                                   \(i) with(df_weib[i,],
                                             data.frame(df_weib[i,],
                                                        value = c(rweibull(floor(prop*sample_size), scale = scale1, shape = shape1), rweibull(sample_size - floor(prop*sample_size), scale = scale2, shape = shape2))))))

for (prop in unique(data_weib_mod_2$prop)){
  print(den_plot_w_mod_2(data_weib_mod_2, prop))
}
```



### Beta Distribution {.tabset}

```{r , include = FALSE}
mod_2_beta_res <- as.data.frame(readRDS( "~/Nadeau/module2_b_all_tests_sim(1000).rds"))

mod_2_beta_res$pwr_range = ifelse(mod_2_beta_res$power <= 0.4,"Low", ifelse(mod_2_beta_res$power <= 0.8, "Medium", "High"))
mod_2_beta_res$pwr_range = factor(mod_2_beta_res$pwr_range, levels = c("High", "Medium", "Low"))

mod_2_beta_res$fp_range = ifelse(mod_2_beta_res$FP <= 0.05,"Preserved", ifelse(mod_2_beta_res$power <= 0.1, "Slightly Inflated", "High"))
mod_2_beta_res$fp_range = factor(mod_2_beta_res$fp_range, levels = c("High", "Slightly Inflated", "Preserved"))

s1_labels <- paste0('s1 = ', unique(mod_2_beta_res$s1))
names(s1_labels) <- unique(mod_2_beta_res$s1)

s2_labels <- paste0('s2 = ', unique(mod_2_beta_res$s2))
names(s2_labels) <- unique(mod_2_beta_res$s2)

```

#### Power
```{r , fig.height=12, fig.width=12, unit='in'}
plot_pwr_b(mod_2_beta_res)
```

#### Power (Interactive Plot)
```{r , fig.height=12, fig.width=12, unit='in'}
plot_pwr_b_inter(mod_2_beta_res)
```

#### False Positive
```{r , fig.height=12, fig.width=12, unit='in'}
plot_fp_b(mod_2_beta_res)
```

#### False Positive (Interactive)
```{r , fig.height=12, fig.width=12, unit='in'}
plot_fp_b_inter(mod_2_beta_res)
```

#### Power with False Positive
```{r , fig.height=12, fig.width=12, unit='in'}
plot_pwr_fp_b(mod_2_beta_res)
```

#### Power with False Positive (Interactive Plot)
```{r , fig.height=12, fig.width=12, unit='in'}
plot_pwr_fp_b_inter(mod_2_beta_res)
```

#### Density Plot
```{r , fig.height=12, fig.width=12, unit='in'}
params_grid <- expand.grid(
  Distribution = c("beta"),
  Alpha = .05,
  Sim = 1,
  nboot = 100,
  SampleSize = 5000,
  Prop = c(0.1, 0.25, 0.5,.75,.9),
  s1 = c(0.25,0.5),
  s2 = c(0.5,.75)
)

df_beta = data.frame(
  dist = params_grid$Distribution,
  sample_size = params_grid$SampleSize,
  prop = params_grid$Prop,
  s1 = params_grid$s1,
  s2 = params_grid$s2
)

data_beta = rbindlist(lapply(seq_len(nrow(df_beta)),
                             \(i) with(df_beta[i,],
                                       data.frame(df_beta[i,],
                                                  value = c(rbeta(sample_size, shape1 = s1, shape2 = s2))))))

s1_labels <- paste0('s1 = ', unique(df_beta$s1))
names(s1_labels) <- unique(df_beta$s1)

s2_labels <- paste0('s2 = ', unique(df_beta$s2))
names(s2_labels) <- unique(df_beta$s2)

print(den_plot_beta_mod_2(data_beta))
```