---
title: "dxsmall_analysis"
author: "Mao Ding"
date: "2023-06-24"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,warning = FALSE,message = FALSE,error = FALSE)
```
## Objective
Perform real world data analysis using BifurcatoR tools to check bimodality
```{r include = FALSE}
#devtools::install_github("VanAndelInstitute/bifurcatoR",force=T)

suppressPackageStartupMessages({
  library(bifurcatoR)
  library(doParallel)
  library(dplyr)
  library(ggplot2)
  library(plotly)
  library(ggpubr)
  library(data.table)
  library(parallel)
  library(mclust)
  library(gtsummary)
  library(tidyverse)
  library(gt)
  library(mixR)
})

```


```{r, include=FALSE}
data(dxsmall)
```
### dxsmall data: pediatric leukemia gene expression values with different fusion groups
```{r, include=TRUE}
show(dxsmall)
```
#### Cohort Characteristics
```{r, include=TRUE}
df = data.frame(colData(dxsmall))
df$Sex = replace(df$Sex, df$Sex == "Unknown", NA)

tbl <- 
  df %>% tbl_summary(type = list(c(AgeGroup, Sex, FAB, fusion, OSI) ~ "categorical",
                               c(BlastPercent, OS) ~ "continuous"),
                   by = FusionGroup,
                   statistic = list(
                     all_continuous() ~ "{mean} ({sd})",
                     all_categorical() ~ "{n} ({p}%)"),
                   digits = all_continuous() ~ 2,
                   label = fusion ~ "Fusion",
                   missing_text = "(Missing)"
                   ) %>%
                   modify_table_styling(
                     columns = label,
                     rows = label == "AYA",
                     footnote = "Adolescent and Young Adult") %>%
                   bold_labels() %>%
                   modify_spanning_header(all_stat_cols() ~ "**Fusion Group**") %>%
                   modify_caption("**Table 1. dxsmall Patient Characteristics** (N= {N})") %>%
                   modify_header(label = "**Variable**")

tbl_highlighted <- 
  as_gt(tbl) %>%
  gt::tab_style(style = list(cell_fill(color = "lightgrey")),
            locations = list(cells_column_labels(),cells_column_spanners())) 
# Target the locations: https://search.r-project.org/CRAN/refmans/gt/html/cells_column_labels.html


print(tbl_highlighted)


```

```{r, include = TRUE}
tbl_highlighted |> gt::gtsave(filename = "/work/larylab/Mao_Ding/bifurcatoR/vignettes/dxsmall/results/dxsmall_Table_1.docx")
```

#### First 10 columns of counts
```{r, include=TRUE}
head(assays(dxsmall)$counts[,1:10],10)
```
#### Summary Statistics of dxsmall counts
```{r, include=TRUE}
summary(t(dxsmall@assays@data@listData$counts))
```
#### First 10 columns of logcounts
```{r, include=TRUE}
head(assays(dxsmall)$logcounts[,1:10],10)
```
#### Summary Statistics of dxsmall logcounts
```{r, include=TRUE}
summary(t(dxsmall@assays@data@listData$logcounts))
```

```{r, include=TRUE}
#rownames(dxsmall)
```

#### rowData: Rows contains their own metadata as a dataframe format to describe their features.
```{r, include=TRUE}
rowData(dxsmall)
```

```{r, include=TRUE}
#head(colnames(dxsmall),20)
```

#### colData: Columns contains their own metadata as a dataframe format to describe their features.
```{r, include=TRUE}
colData(dxsmall)
```

#### Age Group
```{r, fig.width = 6, fig.height = 8, unit='in', include=TRUE}
t_age = table(dxsmall$AgeGroup)
plot_ly(
  x = names(t_age),
  y = as.numeric(t_age), type = "bar", marker = list(color = c("orange"))) %>%
  layout(xaxis = list(title = "Age",
                      zeroline = FALSE),
         yaxis = list(title = "Frequency",
                      zeroline = FALSE))

```
#### Gender
```{r, fig.height=6, fig.width=8, unit='in'}
t_gender = table(dxsmall$Sex)
plot_ly(
  x = names(t_gender),
  y = as.numeric(t_gender), type = "bar") %>%
  layout(xaxis = list(title = "Gender",
                      zeroline = FALSE),
         yaxis = list(title = "Frequency",
                      zeroline = FALSE))
```
#### Fusion Group
```{r, fig.height=8, fig.width=10, unit='in', include=TRUE}
t_fusiongroup = table(dxsmall$FusionGroup)
plot_ly(
  x = names(t_fusiongroup),
  y = as.numeric(t_fusiongroup), type = "bar", marker = list(color = c("lightgreen"))) %>%
  layout(xaxis = list(title = "Fusion Group",
                      zeroline = FALSE,
                      titlefont = list(size = 25)),
         yaxis = list(title = "Frequency",
                      zeroline = FALSE,
                       titlefont = list(size = 25)),
         font = list(size = 18))
```
#### Density Plot of MECOM logcounts in different fusion group
```{r, fig.height=8, fig.width=10, unit='in', include = TRUE}

logcount_mll = logcounts(dxsmall)["MECOM", dxsmall$FusionGroup == "MLL"]
logcount_nsd1 = logcounts(dxsmall)["MECOM", dxsmall$FusionGroup == "NSD1"]

df <- data.frame(
  Fusion_Group = c(rep("MLL", length(logcount_mll)), rep("NSD1", length(logcount_nsd1))),
  logcounts = c(logcount_mll, logcount_nsd1)
)

ggplotly(ggplot(df, aes(x = logcounts, fill = Fusion_Group)) +
           geom_histogram(aes(y = ..density..), position = "identity", alpha = 0.5, bins = 30) +
           geom_density(alpha = 0.5) +
           scale_fill_manual(values = c(2,3)) +  
           theme_minimal () +
           theme(text = element_text(size = 19)) +
           ylab("Density") +
           xlab("MECOM Logcounts"))

```

### Mclust fit: fitting the dataset using a mixture model based on the hypothesis that two clusters exist by specifying group number equals 2.
```{r, include = FALSE}
fit_1 = Mclust(logcount_mll, G = 2)

```


#### mclust fit object density plot in MLL
```{r, include = TRUE}
mb_fit_1 = mclust::mclustBootstrapLRT(logcount_mll, verbose=F, maxG = 1, modelName="E")

```


```{r, include = TRUE}
fit_1_mu1 = round(fit_1$parameters$mean[1],2)
fit_1_sd1 = round((sqrt(fit_1$parameters$variance$sigmasq))[1],2)
fit_1_mu2 = round(fit_1$parameters$mean[2],2)
fit_1_sd2 = round((sqrt(fit_1$parameters$variance$sigmasq))[2],2)
fit_1_prop = round((table(fit_1$classification)/sum(dxsmall$FusionGroup == "MLL"))[1],2)
print(paste0("Mean of the two clusters in MLL are: ",fit_1_mu1,"  ", fit_1_mu2))
print(paste0("SD of the two clusters in MLL are: ",fit_1_sd1,"  ", fit_1_sd2))
print(paste0("Mixing proportion of the two clusters in MLL are: ", fit_1_prop,"  ", 1-fit_1_prop))
print(paste0("The p-value of bimodality in MLL is: ", mb_fit_1$p.value))
```
```{r, fig.height=8, fig.width=10, unit='in', include = TRUE}

plot(fit_1, what="density", xlab = "MECOM Logcounts in MLL", cex.lab = 1.5)
legend_labels <- c(paste0("mu1 = ",fit_1_mu1,"," ," sd1 = ",fit_1_sd1,","," p1 = ",fit_1_prop), 
                   paste0("mu2 = ",fit_1_mu2,"," ," sd2 = ",fit_1_sd2,","," p2 = ",1-fit_1_prop),
                   paste0("p-value = ", mb_fit_1$p.value))

legend("topright", legend = legend_labels, col = c("white","white"), lty= "blank", pch = "", lwd = 0, cex = 1.2, bty = "n")

```

##### Classification for each cell in MLL
```{r, include = TRUE}
head(fit_1$classification,20)
```

##### Uncertainty for each cell in MLL
```{r, include = TRUE}
head(fit_1$uncertainty,20)
```
##### Ameijeiras-Alonso et al. Excess Mass Fit
```{r, include = TRUE}
acr_fit_1 = multimode::modetest(logcount_mll,mod0 = 1,method = "ACR", B = 1000)
acr_fit_1$p.value
```
##### Bimodality Coefficient
```{r, include = TRUE}
library(mousetrap)
bc_fit_1 = mousetrap::mt_check_bimodality(as.data.frame(logcount_mll),method = "BC")
bc_fit_1$BC > 0.555
```
##### Cheng and Hall Excess Mass
```{r, include = TRUE}
ch_fit_1 = multimode::modetest(logcount_mll,mod0 = 1,method = "CH",B = 1000)
ch_fit_1$p.value
```
##### Fisher and Marron Carmer-von Mises
```{r, include = TRUE}
fm_fit_1 = multimode::modetest(logcount_mll,mod0 = 1,method = "FM",B = 1000)
fm_fit_1$p.value
```
##### Hall and York Bandwidth test
```{r, include = TRUE}
hy_fit_1 = multimode::modetest(logcount_mll,mod0 = 1,method = "HY",B = 1000)
hy_fit_1$p.value
```

##### Hartigans' dip test
```{r, include = TRUE}
dip_fit_1 = multimode::modetest(logcount_mll,mod0 = 1,method = "HH",B = 1000)
dip_fit_1$p.value
```

##### Sliverman Bandwidth
```{r, include = TRUE}
sb_fit_1 = multimode::modetest(logcount_mll,mod0 = 1,method = "SI",B = 1000)
sb_fit_1$p.value
```

##### mixR
```{r, fig.height=8, fig.width=10, unit='in', include = TRUE}
mixr_fit_1 = mixfit(logcount_mll, ncomp = 2)
par(cex.lab = 2, cex.axis = 2, cex.main = 2)
p1 = plot(mixr_fit_1, what="density", title = 'MLL Gaussian Mixture (2 components)', cex.main = 20)
p1
p_value_mll = bs.test(logcount_mll, ncomp = c(1,2))$pvalue
print(paste0("The bimodality p-value of MLL is: ", p_value_mll))
```

#### mclust fit object density plot in NSD1

```{r, include = FALSE}
fit_2 = Mclust(logcount_nsd1, G = 2)
mb_fit_2 = mclust::mclustBootstrapLRT(logcount_nsd1, verbose=F, maxG = 1, modelName="E")
```

```{r, include = TRUE}
fit_2_mu1 = round(fit_2$parameters$mean[1],2)
fit_2_sd1 = round((sqrt(fit_2$parameters$variance$sigmasq))[1],2)
fit_2_mu2 = round(fit_2$parameters$mean[2],2)
fit_2_sd2 = round((sqrt(fit_2$parameters$variance$sigmasq))[1],2) # only one sd for fit_2, so set sd2 as same as sd1
fit_2_prop = round((table(fit_2$classification)/sum(dxsmall$FusionGroup == "NSD1"))[1],2)
print(paste0("Mean of the two clusters in NSD1 are: ",fit_2_mu1,"  ", fit_2_mu2))
print(paste0("SD of the two clusters in NSD1 are: ",fit_2_sd1,"  ", fit_2_sd2))
print(paste0("Mixing proportion of the two clusters in NSD1 are: ",fit_2_prop,"  ", 1-fit_2_prop))
print(paste0("The p-value of bimodality in NSD1 is: ", mb_fit_2$p.value))
```

```{r, fig.height=8, fig.width=10, unit='in', include = TRUE}
#### mclust fit object density plot in NSD1

plot(fit_2, what="density", xlab = "MECOM Logcounts in NSD1", cex.lab = 1.5)

legend_labels <- c(paste0("mu1 = ",fit_2_mu1,"," ," sd1 = ",fit_2_sd1,","," p1 = ",fit_2_prop), 
                   paste0("mu2 = ",fit_2_mu2,"," ," sd2 = ",fit_2_sd2,","," p2 = ",1-fit_2_prop),
                   paste0("p-value = ", mb_fit_2$p.value))

legend("topright", legend = legend_labels, col = c("white","white"), lty= "blank", pch = "", lwd = 0, cex = 1.2, bty = "n")

```


```{r, include = TRUE}
##### Classification for Each cell in NSD1
head(fit_2$classification, 20)
```

##### Uncertainty for each cell in NSD1
```{r, include = TRUE}
head(fit_2$uncertainty,20)
```
##### Ameijeiras-Alonso et al. Excess Mass Fit
```{r, include = TRUE}
acr_fit_2 = multimode::modetest(logcount_nsd1,mod0 = 1,method = "ACR", B = 1000)
acr_fit_2$p.value
```
##### Bimodality Coefficient
```{r, include = TRUE}
bc_fit_2 = mousetrap::mt_check_bimodality(as.data.frame(logcount_nsd1),method = "BC")
bc_fit_2$BC > 0.555
```
##### Cheng and Hall Excess Mass
```{r, include = TRUE}
ch_fit_2 = multimode::modetest(logcount_nsd1,mod0 = 1,method = "CH",B = 1000)
ch_fit_2$p.value
```
##### Fisher and Marron Carmer-von Mises
```{r, include = TRUE}
fm_fit_2 = multimode::modetest(logcount_nsd1,mod0 = 1,method = "FM",B = 1000)
fm_fit_2$p.value
```
##### Hall and York Bandwidth test
```{r, include = TRUE}
hy_fit_2 = multimode::modetest(logcount_nsd1,mod0 = 1,method = "HY",B = 1000)
hy_fit_2$p.value
```

##### Hartigans' dip test
```{r, include = TRUE}
dip_fit_2 = multimode::modetest(logcount_nsd1,mod0 = 1,method = "HH",B = 1000)
dip_fit_2$p.value
```

##### Sliverman Bandwidth
```{r, include = TRUE}
sb_fit_2 = multimode::modetest(logcount_nsd1,mod0 = 1,method = "SI",B = 1000)
sb_fit_2$p.value
```
##### mixR
```{r, fig.height=8, fig.width=10, unit='in', include = TRUE}
logcount_nsd1_binned <- bin(logcount_nsd1, brks = seq(min(logcount_nsd1), max(logcount_nsd1), length = 30))
mixr_fit_2 = mixfit(logcount_nsd1, ncomp = 2, ev = TRUE)
p2 = plot(mixr_fit_2, title = 'NSD1 Gaussian Mixture (2 components)', xlim = c(0,6), ylim = c(0,1),cex.lab = 1.5)
p2
p_value_nsd1 = bs.test(logcount_nsd1, ncomp = c(1,2),ev = TRUE)$pvalue
print(paste0("The bimodality p-value of NSD1 is: ", p_value_nsd1))
```

```{r, include=FALSE}
total_cores <- round(parallel::detectCores()*.95)

params_grid_1 <- rbind(expand.grid(
  Distribution = c("norm"),
  Fusion_Group = 'MLL',
  Gene = 'MECOM',
  Alpha = .05,
  Sim = 1000,
  nboot = 1000,
  SampleSize = c(50, 100, 200, 300, 470),
  Prop = fit_1_prop,
  mu1 = fit_1_mu1,
  sd1 = fit_1_sd1,
  mu2 = fit_1_mu2,
  sd2 = fit_1_mu2
))

params_grid_2 <- rbind(expand.grid(
  Distribution = c("norm"),
  Fusion_Group = 'NSD1',
  Gene = 'MECOM',
  Alpha = .05,
  Sim = 1000,
  nboot = 1000,
  
  SampleSize = c(50, 100, 200, 300, 470),
  Prop = fit_2_prop,
  mu1 = fit_2_mu1,
  sd1 = fit_2_sd1,
  mu2 = fit_2_mu2,
  sd2 = fit_2_sd2 
))

params_grid = rbind(params_grid_1, params_grid_2)

process_sims_w_n = function(row){  
  
  if(params_grid$Distribution[row] == "norm"){
    params_list <- list(p = params_grid$Prop[row],
                        mu1 = params_grid$mu1[row],
                        sd1 = params_grid$sd1[row],
                        mu2 = params_grid$mu2[row],
                        sd2 = params_grid$sd2[row])
    
  } else if(params_grid$Distribution[row] == "weib"){
    params_list <- list(p = params_grid$Prop[row],
                        sp1 = mixdist::weibullpar(params_grid$mu1[row],params_grid$sd1[row], loc = 0)$shape,
                        sc1 = mixdist::weibullpar(params_grid$mu1[row],params_grid$sd1[row], loc = 0)$scale,
                        sp2 = mixdist::weibullpar(params_grid$mu2[row],params_grid$sd2[row], loc = 0)$shape,
                        sc2 = mixdist::weibullpar(params_grid$mu2[row],params_grid$sd2[row], loc = 0)$scale)
  }
  output <- bifurcatoR::est_pow(
    n = params_grid$SampleSize[row],
    alpha = params_grid$Alpha[row],
    nsim = params_grid$Sim[row],
    dist = params_grid$Distribution[row],
    params = params_list,
    nboot = params_grid$nboot[row],
    tests = c("dip", "mclust", "mt", "SI","HY","CH","ACR","FM")
  )
  return(cbind(params_grid[row, ], output))
}

```

#### Parameters Grid
```{r, include = TRUE}
params_grid
```

```{r, include=FALSE}
# start.time <- Sys.time()
# results= rbindlist(mclapply(1:nrow(params_grid), function(x) process_sims_w_n(x),mc.cores=total_cores))
# end.time <- Sys.time()
# time.taken <- end.time - start.time
# time.taken
#saveRDS(results,"~/Nadeau/bifurcatorR_Mao_fork/bifurcatoR_Mao_fork/vignettes/module2_dxsmall_norm_all_tests.rds")
```

```{r, include=FALSE}
results = readRDS("/work/larylab/Mao_Ding/bifurcatoR/vignettes/dxsmall/results/raw_results/module2_dxsmall_norm_all_tests.rds")

names(results)[names(results) == "FP"] <- "FPR"

results$delta_mu = round(results$mu2 - results$mu1,2)
results$sd_inflation = round(results$sd2/results$sd1, 2)

results$pwr_range = ifelse(results$power <= 0.4,"Low", ifelse(results$power <= 0.8, "Medium", "High"))
results$pwr_range = factor(results$pwr_range, levels = c("High", "Medium", "Low"))

results$fp_range = ifelse(results$FPR <= 0.05,"Preserved (0 <= FPR <= 0.05)", ifelse(results$FPR <= 0.1, "Slightly Inflated (0.05 < FPR <= 0.1)", "High (0.1 < FPR <= 1)"))
results$fp_range = factor(results$fp_range, levels = c("High (0.1 < FPR <= 1)", "Slightly Inflated (0.05 < FPR <= 0.1)", "Preserved (0 <= FPR <= 0.05)"))

delta_mu_labels <- paste0('Mean Difference = ', unique(results$delta_mu))
names(delta_mu_labels) <- unique(results$delta_mu)

sd_inflation_labels <- paste0('Standard Deviation Ratio = ', unique(results$sd_inflation)," : 1")
names(sd_inflation_labels) <- unique(results$sd_inflation)
```

```{r, include = TRUE}
results$Prop = round(results$Prop,2)
```


#### Power & False Positive
```{r, include=TRUE}
results
```
  
```{r, include=FALSE}
plot_pwr = function(dist,p,fg, df){
    ggplotly(
      ggplot(df[df$Prop==p & df$Distribution == dist & df$Fusion_Group == fg,], aes(SampleSize, power,
                        group = interaction(Test, Distribution),
                        color = Test)) +
    geom_point() +
    geom_line() + 
    
    theme(legend.position = 'none') +
    facet_grid(delta_mu ~ sd_inflation,
               labeller = labeller(delta_mu = delta_mu_labels,
                                   sd_inflation = sd_inflation_labels))+
    theme_classic2(14)+
    scale_color_viridis_d(option = "H")+
    ggtitle(paste0("Mixing Proportion = ", round(unique(results[results$Fusion_Group == fg,]$Prop),2)))+
    ylab("Power") +
    xlab("Sample Size") +
    ylim(0,1)
)
}

plot_fp = function(dist,p,fg,df){
  
ggplotly(
  ggplot(df[df$Prop==p & df$Distribution == dist & df$Fusion_Group == fg,], aes(SampleSize, FPR,
                        group = interaction( Test, Distribution),
                        color = Test)) +
    geom_point() +
    geom_line() +
    geom_hline(yintercept = 0.05, linetype = "dashed", color = "red") +
    scale_y_continuous(breaks = c(0,0.02,0.04,0.05,0.06,0.08,0.10), labels = c(0,0.02,0.04,0.05,0.06,0.08,0.10), limits = c(0,0.1)) +
    theme(legend.position = 'none') +
    facet_grid(delta_mu ~ sd_inflation,
                labeller = labeller(delta_mu = delta_mu_labels,
                                    sd_inflation = sd_inflation_labels)) +
    theme_classic2(14) +
    scale_color_viridis_d(option = "H") +
    ggtitle(paste0("Mixing Proportion = ", round(unique(results[results$Fusion_Group == fg,]$Prop),2))) +
    ylab("False Positive Rate")
)
}
```

```{r, include = FALSE} 
### Power with FPR ###
# set.seed(2023)
# plot_pwr_fp = function(df,fg){
#   ggplot((df[df$Fusion_Group == fg,]) %>% 
#            mutate(x = jitter(SampleSize, factor = 2), y = jitter(power, factor = 0)), 
#          aes(x = x, y = y, group = interaction(Test, Distribution), color = Test)) +
#     geom_point(aes(size = 5, shape = fp_range, color = Test)) +
#     geom_line() +
#     labs(shape = "FP Range") +
#     scale_shape_manual(values = c("Preserved (0 <= FP <= 0.05)" = 20, "Slightly Inflated (0.05 < FP <= 0.1)" = 9, "High (0.1 < FP <= 1)" = 2)) +
#     theme(legend.position = 'right') +
#     facet_grid(delta_mu ~ sd_inflation,
#                labeller = labeller(delta_mu = delta_mu_labels,
#                                    sd_inflation = sd_inflation_labels),scales="free") +
#     theme_classic(14) +
#     scale_color_viridis_d(option = "H") +
#     scale_x_continuous(trans = "log2", breaks = c(50, 100, 200, 300, 400, 500), labels = c(50, 100, 200, 300, 400, 500)) +
#     ggtitle(paste0("Mixing Proportion = ", round(unique((df[df$Fusion_Group == fg,])$Prop),2))) +
#     xlab("Sample Size") +
#     ylab("Power") +
#     scale_size(guide = "none")
# }

```

```{r, include = FALSE} 
### Power with FP (Zach's style) ###
set.seed(2023)
plot_pwr_fp = function(df,fg){
  ggplot2::ggplot((df[df$Fusion_Group == fg,]) %>% 
           mutate(x = jitter(SampleSize, factor = 0), y = jitter(power, factor = 0)), 
         aes(x = x, y = y, group = interaction(Test, Distribution), color = Test, size = FPR)) +
    geom_point(position = position_dodge2(width = .5)) +
    geom_line(linewidth=0.4,position = position_dodge2(width = .5)) +
    theme(legend.position = 'none') +
    facet_grid(delta_mu ~ sd_inflation,
               labeller = labeller(delta_mu = delta_mu_labels,
                                   sd_inflation = sd_inflation_labels),scales="free") +
    theme_classic2(16)+
    #theme(text = element_text(size = 16)) +
    scale_color_viridis_d(option = "H")+
    #scale_color_manual(values=unname(mypal)) +
    scale_size_continuous(breaks=c(0.01,0.05,0.1,0.5,1),range=c(3,0),limits=c(0.00001,1)) +
    ggtitle(paste0("Sampling Ratio = ", round(unique((df[df$Fusion_Group == fg,])$Prop),2) *100, ":", 
                   100 - round(unique((df[df$Fusion_Group == fg,])$Prop),2)*100)) +
    ylab("Power") + xlab("N") + 
    scale_y_continuous(limits=c(0,1),breaks=seq(0,1,0.2)) +
    scale_x_continuous(trans = "log2", breaks = c(50, 100, 200, 300, 400, 500), labels = c(50, 100, 200, 300, 400, 500)) +
    geom_hline(yintercept = 0.8, linetype=2,alpha=0.2)
    
}

```



```{r, include=FALSE}
### Power with FP (Interactive) ###
set.seed(2023)
plot_pwr_fp_inter = function(df,fg){
  p = ggplotly(
    ggplot((df[df$Fusion_Group == fg,]) %>%
           mutate(x = jitter(SampleSize, factor = 2), y = jitter(power, factor = 0)),
         aes(x = x, y = y, group = interaction(Test, Distribution), color = Test)) +
    geom_point(aes(size = 5, shape = fp_range, color = Test)) +
    geom_line() +
    labs(shape = "FP Range") +
    scale_shape_manual(values = c("Preserved (0 <= FP <= 0.05)" = 20, "Slightly Inflated (0.05 < FP <= 0.1)" = 9, "High (0.1 < FP <= 1)" = 2)) +
    theme(legend.position = 'right') +
    facet_grid(delta_mu ~ sd_inflation,
               labeller = labeller(delta_mu = delta_mu_labels,
                                   sd_inflation = sd_inflation_labels),scales="free") +
    theme_classic(14) +
    scale_color_viridis_d(option = "H") +
    scale_x_continuous(trans = "log2", breaks = c(50, 100, 200, 300, 400, 500), labels = c(50, 100, 200, 300, 400, 500)) +
    ggtitle(paste0("Mixing Proportion = ", round(unique((df[df$Fusion_Group == fg,])$Prop),2))) +
    xlab("Log(Sample Size)") +
    ylab("Power") +
    scale_size(guide = "none"))


    df= data.frame(id = seq_along(p$x$data), legend_entries = unlist(lapply(p$x$data, `[[`, "name")))
  df$legend_group <- sapply(df$legend_entries, function(x) strsplit(gsub("^\\(|\\)$", "", x),",")[[1]][1])
  df$is_first <- !duplicated(df$legend_group)

  for (i in df$id) {
    # Is the layer the first entry of the group?
    is_first <- df$is_first[[i]]
    # Assign the group identifier to the name and legendgroup arguments
    p$x$data[[i]]$name <- df$legend_group[[i]]
    p$x$data[[i]]$legendgroup <- p$x$data[[i]]$name
    # Show the legend only for the first layer of the group
    if (!is_first) p$x$data[[i]]$showlegend <- FALSE
  }
return (p)
}
```


## Fusion Group = MLL{.tabset}
### Power {.tabset}
```{r ,fig.height=8, fig.width=10, unit='in'}
plot_pwr(dist="norm",p = results$Prop, fg = "MLL", results)
```

### False Positive {.tabset}
```{r ,fig.height=8, fig.width=10, unit='in'}
plot_fp(dist="norm",p = results$Prop, fg = "MLL", results)
```

### Power with False Positive {.tabset}
```{r ,fig.height=8, fig.width=11, unit='in'}
plot_pwr_fp(df = results, fg = "MLL")
```


```{r ,fig.height=6, fig.width=10, unit='in',include = FALSE}
### Power with False Positive Interactive {.tabset}
plot_pwr_fp_inter(df = results, fg = "MLL")
```



```{r, include=FALSE}
### Comparing Methods in MLL
mll = results[results$Fusion_Group == "MLL",] %>%
  group_by(Test) %>%
  summarise(avg_power = mean(power), avg_fp = mean(FPR))

mll$rank_power = rank(-mll$avg_power, ties.method = "min")
mll$rank_fp = rank(mll$avg_fp)

mll <- mll[order(-mll$avg_power, mll$avg_fp), ]
mll
```


## Fusion Group = NSD1{.tabset}
### Power {.tabset}
```{r ,fig.height=8, fig.width=10, unit='in'}
plot_pwr(dist="norm",p = results$Prop, fg = "NSD1", results)
```

### False Positive {.tabset}
```{r ,fig.height=8, fig.width=10, unit='in'}
plot_fp(dist="norm",p = results$Prop, fg = "NSD1", results)
```

### Power with False Positive {.tabset}
```{r ,fig.height=8, fig.width=11, unit='in'}
plot_pwr_fp(df = results, fg = "NSD1")
```

```{r ,fig.height=6, fig.width=10, unit='in', include = FALSE}
### Power with False Positive Interactive {.tabset}
plot_pwr_fp_inter(df = results, fg = "NSD1")
```


```{r, include=FALSE}
### Comparing Methods in NSD1
nsd1 = results[results$Fusion_Group == "NSD1",] %>%
  group_by(Test) %>%
  summarise(avg_power = mean(power), avg_fp = mean(FPR))

nsd1$rank_power = rank(-nsd1$avg_power, ties.method = "min")
nsd1$rank_fp = rank(nsd1$avg_fp)

nsd1 <- nsd1[order(-nsd1$avg_power, nsd1$avg_fp), ]
nsd1

```
